SUPPLEMENTARY:\\A new approach to bias correction in high-throughput sequencing data

### 2012-01-03 seqbias-supplement.tex
Final paper, let's hope.

\section{Total numbers of reads used to train each method}

@@

In this section and the next, we present some theoretical analysis quantifying
the accuracy of parameter estimation and the likelihood of falsely learning a
biased model from unbiased data.

@@

As discussed in Supplementary Section 9.2, $2n D$ is approximated by a $\chi^2$
distribution with 3 degrees of freedom for large $n$, and so we can estimate
this probability for various values of $n$. This is shown in Figure
\ref{fig:nepr}. From this figure we can see, for example, that training with
more than 10,000 reads results in an incorrect non-empty model with probability
less than 0.0004.

For small $n$, the upper bound on non-empty model probability is much higher.
In our tests, this upper bound is not tight for a small number of reads. We
trained the model on 100 sets of 100 simulated reads, drawn uniformly at random
from exonic sequences and in only 3 trials was a non-empty model trained, far
less than the upper bound expectation of 23 out of 100. This test was repeated
using sets of 10,000 reads, and in no trial was a non-empty model trained.  From
these results, and the results in Supplementary Section 5, we recommend training
our method with at least 10,000 reads.

>>>>

\section{Total Numbers of Reads Used to Train Each Method}

@@

In this section and the next, we present some theoretical analysis quantifying
the accuracy of parameter estimation and the likelihood of falsely learning a
biased model from unbiased data. These results follow mostly from work
originally done by Birch \cite{Birch1964}, but are presented here for
completeness, and in a manner more directly addressing the the question at hand.

@@

As discussed in Supplementary Section 10.2, $2n D$ is approximated by a $\chi^2$
distribution with 3 degrees of freedom for large $n$, and so we can estimate
this probability for various values of $n$. This is shown in Figure
\ref{fig:nepr}. From this figure we can see, for example, that training with
more than 10,000 reads results in an incorrect non-empty model with probability
less than 0.0004.

For small $n$, the upper bound on non-empty model probability is much higher.
In our tests, this upper bound is not tight for a small number of reads. We
trained the model on 100 sets of 100 simulated reads, drawn uniformly at random
from exonic sequences and in only 3 trials was a non-empty model trained, far
less than the upper bound expectation of 23 out of 100. This test was repeated
using sets of 10,000 reads, and in no trial was a non-empty model trained.  From
these results, and the results in Supplementary Section 6, we recommend training
our method with at least 10,000 reads.
